A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-31 papers/paper1/ms.tex
Moved CSV files, created new notebook, and added more citations to paper

\begin{deluxetable*}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition\\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  \citet{2018ApJ...853..122R} & - & TLSE \\
  \citet{Kochukhov21} & - & Magnetic fields of M dwarfs \\
  \citet{2021sf2a.conf..363B} & - & Stellar rotation using ROOSTER \\
  \citet{2015MNRAS.450.3211A} & - & Using Kepler to study stellar rotation \\
  \citet{2022ApJ...927..219C} & - & Using deep learning to recover TESS light curves \\
  \citet{2021AJ....162..123L} & - & Test Lightcurve and study stellar surfaces \\
  \citet{2022ApJ...925..185D} & - & Lightcurves for oblate, rapid rotators \\
  \citet{Reinhold2013} & - & Measure rotation of active Kepler Stars \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\  
  \enddata
\end{deluxetable*}

@@

\begin{figure*}[!htb]
  \centering
  \includegraphics[scale=0.5]{Amplitude Comparison Mask.png}
  \caption{The mask showing how we determined which points to keep and which ones were outliers.}
\end{figure*}
\FloatBarrier

@@

% TESS - 0.104
% Kepler - 0.00697

@@

\begin{figure}
  \gridline{\fig{figures/Kepler_contrast.png}{0.3\textwidth}{(a)}}
  \gridline{\fig{figures/TESS_contrast.png}{0.3\textwidth}{(b)}}
  \gridline{\fig{one_minus_ratio.png}{0.3\textwidth}{(c)}}
  \caption{A nice inverted pyramid figure
    consisting of six individual files}
\end{figure}

>>>>

\begin{deluxetable*}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{2015MNRAS.450.3211A} & - & Using Kepler to study stellar rotation \\
  \citet{2022ApJ...924...31B} & - & Estimating the lifetime of starspots based on rotational periods \\
  \citet{2010ApJ...713L.109B} & - & Why Kepler picked particular stars for observation \\
  \citet{2010Sci...327..977B} & - & Using the Kepler mission to discover exoplanets \\
  \citet{2021sf2a.conf..363B} & - & Stellar rotation using ROOSTER \\
  \citet{2022ApJ...927..219C} & - & Deep learning to recover TESS light curves \\
  \citet{2022ApJ...925..185D} & - & Lightcurves for oblate, rapid rotators \\
  \citet{2017ARep...61..122D} & - & Using Kepler to observe starspots on M dwarf stars \\
  \citet{2020RAA....20..167F} & - & Overview of Kepler mission \\
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition \\
  \citet{Kochukhov21} & - & Magnetic fields of M dwarfs \\
  \citet{2021AJ....162..123L} & - & Test Lightcurve and study stellar surfaces \\
  \citet{2022ApJ...933..195M} & - & Comparing rotational periods of sun-like stars versus photometric amplitude \\
  \citet{2020MNRAS.491.2706N} & - & Calculating stellar age based on starspot covering fraction \\
  \citet{2018ApJ...853..122R} & - & TLSE \\
  \citet{Reinhold2013} & - & Measure rotation of active Kepler Stars \\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  \citet{2022MNRAS.511.2285W} & - & Starspots on detached eclipsing binaries (DEBs) \\
  \enddata
\end{deluxetable*}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{Amplitude Comparison Mask.png}
  \caption{The mask showing how we determined which points to keep and which ones were outliers.}
\end{figure}
\FloatBarrier

@@

@@

\begin{figure*}
  \gridline
    {\fig{figures/Kepler_contrast.png}{0.3\textwidth}{(a)}
    {\fig{figures/TESS_contrast.png}{0.3\textwidth}{(b)}}
    {\fig{one_minus_ratio.png}{0.3\textwidth}{(c)}}}
  \caption{A nice inverted pyramid figure
    consisting of six individual files}
\end{figure*}
